---
pagetitle: "Census 2021: Education"
lang: "en-GB"
output:
  html_document:
    css: ../../guidance/template/styles.css
    self_contained: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse) ; library(htmltools) ; library(DT) 

df <- read_csv("2021_highest_level_qualification_la_gm.csv") %>%
    rename_all(. %>% str_to_title() %>% str_replace_all("_", " "))
```
<header>
<span id="a11yNav"><a href="#downloads" class="themeBlockDark">Skip to downloads</a></span>
<a href="https://www.trafforddatalab.io/data.html"><img src="https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg" alt="Trafford Data Lab" aria-label="Return to Trafford Data Lab data page" width="100" class="traffordDataLabLogo"/></a>

<h1>Census 2021: Education</h1>
*Census 2021 estimates that classify usual residents in England and Wales aged 16 years and over who have academic, vocational, or professional qualifications, as well as the number of schoolchildren and full-time students.*

</header>

<main>
<h2>Metadata</h2>

<table id="metadata" class="table table-condensed">
  <thead>
    <tr class="header">
      <th>Source</th>
      <th>Publisher</th>
      <th>Time period</th>
      <th>Geography</th>
      <th>Licence</th>
      <th>Attribution</th>
      <th>Last updated</th>
    </tr>
  </thead>
  <tr>
    <td><a href="https://www.ons.gov.uk/releases/educationcensus2021inenglandandwales" target="_blank">Office for National Statistics</a></td>
    <td><a href="https://www.ons.gov.uk" target="_blank">Office for National Statistics</a></td>
    <td><time datetime="2021-03-21">2021-03-21</time></td>
    <td>Local authority (<abbr>LA<abbr>), Middle-layer Super Output Area (<abbr>MSOA</abbr>), Lower-layer Super Output Area (<abbr>LSOA</abbr>), Output Area (<abbr>OA</abbr>)</td>
    <td><a href="http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/" target="_blank">OGL v3.0</a></td>
    <td>Contains public sector information licensed under the Open Government Licence v3.0</td>
    <td><time datetime="2023-01-16">2023-01-16</time></td>
  </tr>
</table>

<h2>Preview</h2>
Sort, filter and export a selection of the data using the table.

```{r preview}
datatable(df, 
          class = 'cell-border stripe',
          rownames = FALSE, 
          extensions = c('Scroller', 'Buttons', 'KeyTable'),
          options = list(
            keys = TRUE,
            search = list(regex = TRUE),
            searchHighlight = TRUE,
            dom = 'ftB',
            buttons = list(
              list(extend = "csv", 
                   text = "Download selection")),
            deferRender = TRUE,
            scrollX = TRUE,
            scrollY = 300,
            scroller = TRUE,
            columnDefs = list(
              list(className = 'dt-left', targets = "_all")
              )))
```
<div id="tableFooterTitle">Residents aged 16 years and over of Local Authorities in Greater Manchester classified by highest level of qualification held.</div>

<h2>Data</h2>
<span id ="downloads">Download the complete datasets in Comma Separated Values (<abbr>CSV</abbr>) format using the following links:</span>

|File name |Geography |
|---|---|
|[2021_highest_level_qualification_la_gm.csv](2021_highest_level_qualification_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_highest_level_qualification_msoa_trafford.csv](2021_highest_level_qualification_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_highest_level_qualification_lsoa_trafford.csv](2021_highest_level_qualification_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_highest_level_qualification_oa_trafford.csv](2021_highest_level_qualification_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |
|[2021_schoolchildren_and_full-time_students_la_gm.csv](2021_schoolchildren_and_full-time_students_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_schoolchildren_and_full-time_students_msoa_trafford.csv](2021_schoolchildren_and_full-time_students_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_schoolchildren_and_full-time_students_lsoa_trafford.csv](2021_schoolchildren_and_full-time_students_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_schoolchildren_and_full-time_students_oa_trafford.csv](2021_schoolchildren_and_full-time_students_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |

<h2>Pre-processing</h2>
[The R script used to process the data](pre-processing.R) can be adapted to other areas. For information about R visit the <a href="https://cran.r-project.org" target="_blank">CRAN website</a>.

</main>

<script>
  // Fixes to dynamic elements created by DataTables to improve accessibility
  var removeElFn = setInterval(removeElement, 1000);
  
  function removeElement() {
    try {
      var el = document.getElementsByClassName("dataTables_scrollBody")[0].childNodes[0];
      el.removeChild(el.childNodes[0]); // Remove unwanted hidden text element from table - causing accessibility alert as it has no label
      
      el.parentNode.setAttribute('tabindex', '0');  // add attribute allowing keyboard users to access scrollable area
      
      clearInterval(removeElFn);  // cancel any further calls to this function as we have completed all actions
    }
    catch(e) {
      // form element 'el' doesn't exist yet so setInterval will call the function again until it does
    }
  }
</script>