---
title: "CCTV"
output:
  html_document:
    css: ../guidance/template/styles.css
    self_contained: TRUE
---

<a href="https://www.trafforddatalab.io/data"><img src="https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg" alt="Trafford Data Lab" width="100" border="0" style="position:absolute; top:0; right:0; padding:5px;"/></a>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse) ; library(htmltools) ; library(DT) 

df <- read_csv("trafford_cctv_cameras.csv") %>% 
  select(-area_name, -area_code) %>% 
  rename_all(. %>% str_to_title() %>% str_replace_all("_", " "))
```

*The location of Local Authority controlled CCTV cameras in Trafford.*

<br />

## Metadata

|Source |Publisher |Time period |Geography |Licence |Attribution |Last updated |
|:---|:---|:---|:---|:---|:---|:---|
|Trafford Council |<a href="https://www.trafforddatalab.io/open_data/cctv" target="_blank">Trafford Council</a> |2018-05 |Point data |<a href="http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/" target="_blank">OGL v3.0</a> |Contains public sector information licensed under the Open Government Licence v3.0 |2019-04-12 |

## Preview
Sort, filter and export a selection of the data using the table. An <a href="https://www.trafforddatalab.io/explore/#dataset=cctv" target="_blank">interactive map</a> is also available.

```{r preview}
datatable(df, 
          class = 'cell-border stripe',
          rownames = FALSE, 
          filter = 'top',
          caption = tags$caption(
            style = 'caption-side: bottom; text-align: center; color: #555555;',
            em("Table caption")),
          width = "100%",
          extensions = c('Scroller', 'Buttons', 'KeyTable'),
          options = list(
            keys = TRUE,
            search = list(regex = TRUE),
            searchHighlight = TRUE,
            dom = 'tipB',
            buttons = list(
              list(extend = "csv", 
                   text = "Download selection")),
            deferRender = TRUE,
            scrollX = TRUE,
            scrollY = 300,
            scroller = TRUE,
            autoWidth = TRUE,
            columnDefs = list(
              list(className = 'dt-left', targets = "_all"),
              list(targets = c(0,2,3), searchable = FALSE)
              )))
```

## Data
Download the complete dataset using the links below.

|File name |Format |
|:---|:---|
|[trafford_cctv_cameras](trafford_cctv_cameras.csv) |CSV |
|[trafford_cctv_cameras](trafford_cctv_cameras.geojson) |GeoJSON |

## Pre-processing
The <a href="https://cran.r-project.org" target="_blank">R</a> [script](pre-processing.R) used to process the data can adapted to other areas.

<br />