---
pagetitle: "Wholesale food businesses"
lang: "en-GB"
output:
  html_document:
    css: ../guidance/template/styles.css
    self_contained: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse) ; library(htmltools) ; library(DT) 
df <- read_csv("trafford_wholesale_food_businesses.csv")
```

<header>
<span id="a11yNav"><a href="#downloads" class="themeBlockDark">Skip to downloads</a></span>
<a href="https://www.trafforddatalab.io/data.html"><img src="https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg" alt="Trafford Data Lab" aria-label="Return to Trafford Data Lab data page" width="100" class="traffordDataLabLogo"/></a>

<h1>Wholesale food businesses</h1>
*Wholesale food businesses in Trafford supplying food of animal origin that require approval by the Food Standards Agency under Regulation 853/2004*

</header>

<main>
<h2>Metadata</h2>

<table id="metadata" class="table table-condensed">
  <thead>
    <tr class="header">
      <th>Source</th>
      <th>Publisher</th>
      <th>Time period</th>
      <th>Geography</th>
      <th>Licence</th>
      <th>Attribution</th>
      <th>Last updated</th>
    </tr>
  </thead>
  <tr>
    <td>Food Standards Agency</td>
    <td><a href="https://www.food.gov.uk/business-guidance/approved-food-establishments" target="_blank">Food Standards Agency</a></td>
    <td><time datetime="2020-07-01">2020-07-01</time></td>
    <td>Point data</td>
    <td><a href="http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/" target="_blank">OGL v3.0</a></td>
    <td>Contains public sector information licensed under the Open Government Licence v3.0</td>
    <td><time datetime="2020-07-17">2020-07-15</time></td>
  </tr>
</table>

<h2>Preview</h2>
Sort, filter and export a selection of the data using the table.

```{r preview}
datatable(df, 
          class = 'cell-border stripe',
          rownames = FALSE, 
          extensions = c('Scroller', 'Buttons', 'KeyTable'),
          options = list(
            keys = TRUE,
            search = list(regex = TRUE),
            searchHighlight = TRUE,
            dom = 'ftB',
            buttons = list(
              list(extend = "csv", 
                   text = "Download selection")),
            deferRender = TRUE,
            scrollX = TRUE,
            scrollY = 300,
            scroller = TRUE,
            autoWidth = TRUE, # ONLY REQUIRED IF COLUMNS SCROLL HORIZONTALLY
            columnDefs = list(
              list(className = 'dt-left', targets = "_all")
              # , list(targets = 0, searchable = FALSE) stop filtering
              )))
```
<div id="tableFooterTitle">Wholesale food businesses in Trafford supplying food of animal origin</div>

<h2>Data</h2>
<span id ="downloads">Download the complete dataset using the following links:</span>

|File name |Format |
|---|---|
|[trafford_wholesale_food_businesses.csv](trafford_wholesale_food_businesses.csv) |CSV |
|[trafford_wholesale_food_businesses.geojson](trafford_wholesale_food_businesses.geojson) |GeoJSON |

<h2>Pre-processing</h2>
[The R script used to process the data](pre-processing.R) can be adapted to other areas. For information about R visit the <a href="https://cran.r-project.org" target="_blank">CRAN website</a>.

</main>

<script>
  // Fixes to dynamic elements created by DataTables to improve accessibility
  var removeElFn = setInterval(removeElement, 1000);
  
  function removeElement() {
    try {
      var el = document.getElementsByClassName("dataTables_scrollBody")[0].childNodes[0];
      el.removeChild(el.childNodes[0]); // Remove unwanted hidden text element from table - causing accessibility alert as it has no label
      
      el.parentNode.setAttribute('tabindex', '0');  // add attribute allowing keyboard users to access scrollable area
      
      clearInterval(removeElFn);  // cancel any further calls to this function as we have completed all actions
    }
    catch(e) {
      // form element 'el' doesn't exist yet so setInterval will call the function again until it does
    }
  }
</script>