---
pagetitle: "Census 2021: Population estimates"
lang: "en-GB"
output:
  html_document:
    css: ../../guidance/template/styles.css
    self_contained: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse) ; library(htmltools) ; library(DT)

df <- read_csv("2021_population_by_sex_and_age_group_wide_la_gm.csv") %>%
    rename(`0-15` = aged_0_to_15,
           `16-64` = aged_16_to_64,
           `65+` = aged_65_and_over) %>%
    rename_all(. %>% str_to_title() %>% str_replace_all("_", " "))
```
<header>
<span id="a11yNav"><a href="#downloads" class="themeBlockDark">Skip to downloads</a></span>
<a href="https://www.trafforddatalab.io/data.html"><img src="https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg" alt="Trafford Data Lab" aria-label="Return to Trafford Data Lab data page" width="100" class="traffordDataLabLogo"/></a>

<h1>Census 2021: Population estimates</h1>
*Census 2021 estimates of the usual resident population in Trafford and Greater Manchester.*

</header>

<main>
<h2>Metadata</h2>

<table id="metadata" class="table table-condensed">
  <thead>
    <tr class="header">
      <th>Source</th>
      <th>Publisher</th>
      <th>Time period</th>
      <th>Geography</th>
      <th>Licence</th>
      <th>Attribution</th>
      <th>Last updated</th>
    </tr>
  </thead>
  <tr>
    <td>Office for National Statistics</td>
    <td><a href="https://www.ons.gov.uk/census" target="_blank">Office for National Statistics</a></td>
    <td><time datetime="2021-03-21">2021-03-21</time></td>
    <td>Local authority (<abbr>LA<abbr>), Middle-layer Super Output Area (<abbr>MSOA</abbr>), Lower-layer Super Output Area (<abbr>LSOA</abbr>), Output Area (<abbr>OA</abbr>), Electoral Ward (<abbr>Ward</abbr>)</td>
    <td><a href="http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/" target="_blank">OGL v3.0</a></td>
    <td>Contains public sector information licensed under the Open Government Licence v3.0</td>
    <td><time datetime="2023-06-02">2023-06-02</time></td>
  </tr>
</table>

<h2>Preview</h2>
Sort, filter and export a selection of the data using the table.

```{r preview}
datatable(df,
          class = 'cell-border stripe',
          rownames = FALSE,
          extensions = c('Scroller', 'Buttons', 'KeyTable'),
          options = list(
            keys = TRUE,
            search = list(regex = TRUE),
            searchHighlight = TRUE,
            dom = 'ftB',
            buttons = list(
              list(extend = "csv",
                   text = "Download selection")),
            deferRender = TRUE,
            scrollX = TRUE,
            scrollY = 300,
            scroller = TRUE,
            columnDefs = list(
              list(className = 'dt-left', targets = "_all")
              )))
```
<div id="tableFooterTitle">2021 population estimates for Greater Manchester authorities (wide layout)</div>

<h2>Data</h2>
<span id ="downloads">Download the complete datasets in Comma Separated Values (<abbr>CSV</abbr>) format using the following links:</span>

<h3>Population by sex and age (Persons)</h3>
|File name |Geography |
|---|---|
|[2021_population_by_sex_and_age_group_wide_la_gm.csv](2021_population_by_sex_and_age_group_wide_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_population_by_sex_and_age_la_gm.csv](2021_population_by_sex_and_age_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_population_by_sex_and_age_msoa_trafford.csv](2021_population_by_sex_and_age_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_population_by_sex_and_age_lsoa_trafford.csv](2021_population_by_sex_and_age_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_population_by_sex_and_age_ward_trafford.csv](2021_population_by_sex_and_age_ward_trafford.csv) |<abbr title="Electoral Ward">Ward</abbr> |

<h3>Population by sex and age group time series 1981-2021 (Persons)</h3>
|File name |Geography |
|---|---|
|[1981-2021_population_by_sex_and_age_group_la_gm.csv](1981-2021_population_by_sex_and_age_group_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[1981-2021_population_by_sex_and_age_group_la_trafford.csv](1981-2021_population_by_sex_and_age_group_la_trafford.csv) |<abbr title="Local Authority">LA</abbr> |

<h3>Population by five-year age bands (Persons)</h3>
|File name |Geography |
|---|---|
|[2021_population_by_5_year_age_bands_la_gm.csv](2021_population_by_5_year_age_bands_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_population_by_5_year_age_bands_msoa_trafford.csv](2021_population_by_5_year_age_bands_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_population_by_5_year_age_bands_lsoa_trafford.csv](2021_population_by_5_year_age_bands_lsoa_trafford.cs) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_population_by_5_year_age_bands_oa_trafford.csv](2021_population_by_5_year_age_bands_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |

<h3>Population by sex (Persons)</h3>
|File name |Geography |
|---|---|
|[2021_population_by_sex_la_gm.csv](2021_population_by_sex_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_population_by_sex_msoa_trafford.csv](2021_population_by_sex_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_population_by_sex_lsoa_trafford.csv](2021_population_by_sex_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_population_by_sex_oa_trafford.csv](2021_population_by_sex_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |
|[2021_population_by_sex_ward_trafford.csv](2021_population_by_sex_ward_trafford.csv) |<abbr title="Electoral Ward">Ward</abbr> |

<h3>Population density (Persons)</h3>
|File name |Geography |
|---|---|
|[2021_population_density_la_gm.csv](2021_population_density_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_population_density_msoa_trafford.csv](2021_population_density_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_population_density_lsoa_trafford.csv](2021_population_density_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_population_density_oa_trafford.csv](2021_population_density_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |
|[2021_population_density_ward_trafford.csv](2021_population_density_ward_trafford.csv) |<abbr title="Electoral Ward">Ward</abbr> |

<h3>Population density time series 1981-2021 (Persons)</h3>
|File name |Geography |
|---|---|
|[1981-2021_population_density_la_gm.csv](1981-2021_population_density_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |

<h3>Household composition (Households)</h3>
|File name |Geography |
|---|---|
|[2021_household_composition_la_gm.csv](2021_household_composition_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_household_composition_msoa_trafford.csv](2021_household_composition_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_household_composition_lsoa_trafford.csv](2021_household_composition_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_household_composition_oa_trafford.csv](2021_household_composition_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |
|[2021_household_composition_ward_trafford.csv](2021_household_composition_ward_trafford.csv) |<abbr title="Electoral Ward">Ward</abbr> |

<h3>Household size (Households)</h3>
|File name |Geography |
|---|---|
|[2021_household_size_la_gm.csv](2021_household_size_la_gm.csv) |<abbr title="Local Authority">LA</abbr> |
|[2021_household_size_msoa_trafford.csv](2021_household_size_msoa_trafford.csv) |<abbr title="Middle-layer Super Output Area">MSOA</abbr> |
|[2021_household_size_lsoa_trafford.csv](2021_household_size_lsoa_trafford.csv) |<abbr title="Lower-layer Super Output Area">LSOA</abbr> |
|[2021_household_size_oa_trafford.csv](2021_household_size_oa_trafford.csv) |<abbr title="Output Area">OA</abbr> |
|[2021_household_size_ward_trafford.csv](2021_household_size_ward_trafford.csv) |<abbr title="Electoral Ward">Ward</abbr> |

<h2>Pre-processing</h2>
The R scripts used to process the data for the [2021 population and household data releases](pre-processing.R) and the [1981-2021 time series datasets](pre-processing-time-series.R) can be adapted to other areas. For information about R visit the <a href="https://cran.r-project.org" target="_blank">CRAN website</a>.

</main>

<script>
  // Fixes to dynamic elements created by DataTables to improve accessibility
  var removeElFn = setInterval(removeElement, 1000);

  function removeElement() {
    try {
      var el = document.getElementsByClassName("dataTables_scrollBody")[0].childNodes[0];
      el.removeChild(el.childNodes[0]); // Remove unwanted hidden text element from table - causing accessibility alert as it has no label

      el.parentNode.setAttribute('tabindex', '0');  // add attribute allowing keyboard users to access scrollable area

      clearInterval(removeElFn);  // cancel any further calls to this function as we have completed all actions
    }
    catch(e) {
      // form element 'el' doesn't exist yet so setInterval will call the function again until it does
    }
  }
</script>
