---
pagetitle: "Trafford Council local election results"
lang: "en-GB"
output:
  html_document:
    css: ../guidance/template/styles.css
    self_contained: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse) ; library(htmltools) ; library(DT) 

df <- read_csv("trafford_council_election_results.csv") %>% 
  rename_all(. %>% str_to_title() %>% str_replace_all("_", " "))
```

<header>
<a href="https://www.trafforddatalab.io/data"><img src="https://www.trafforddatalab.io/assets/logo/trafforddatalab_logo.svg" alt="Trafford Data Lab" width="100" border="0" style="position:absolute; top:0; right:0; padding:5px;"/></a>

# Trafford Council local election results
*Results from Trafford council local elections/by-elections from 2016 onwards*
<br />
</header>
<main>
## Metadata

|Source |Publisher |Time period |Geography |Licence |Attribution |Last updated |
|:---|:---|:---|:---|:---|:---|:---|
|Trafford Council |<a href="https://www.trafford.gov.uk/about-your-council/elections/election-results.aspx" target="_blank">Trafford Council</a> |2016 - 2019 |Electoral Ward |<a href="http://www.nationalarchives.gov.uk/doc/open-government-licence/version/3/" target="_blank">OGL v3.0</a> |Contains public sector information licensed under the Open Government Licence v3.0 |2019-07-09 |

## Preview
Sort, filter and export a selection of the data using the table. Visualisations can be found in our <a href="https://github.com/traffordDataLab/analysis/tree/master/local_election" target="_blank">analysis repository</a> on GitHub.

```{r preview}
datatable(df, 
          class = 'cell-border stripe',
          rownames = FALSE, 
          extensions = c('Scroller', 'Buttons', 'KeyTable'),
          options = list(
            keys = TRUE,
            search = list(regex = TRUE),
            searchHighlight = TRUE,
            dom = 'ftB',
            buttons = list(
              list(extend = "csv", 
                   text = "Download selection")),
            deferRender = TRUE,
            scrollX = TRUE,
            scrollY = 300,
            scroller = TRUE,
            autoWidth = TRUE,
            columnDefs = list(
              list(className = 'dt-left', targets = "_all")
              )))
```
<div style="text-align: center; color: #555;">
  <em>Results from Trafford council local elections/by-elections</em>
</div>

## Data
Download the complete dataset using the links below.

|File name |Format |
|:---|:---|
|[trafford_council_election_results](trafford_council_election_results.csv) |CSV |

## Notes
Conforms to the specification described in the <a href="http://e-sd.org/vgTJ3" target="_blank">local transparency guidance - publishing elections results data</a> document by the Local Government Association. Validated using the <a href="https://validator.opendata.esd.org.uk/electionresults" target="_blank">Local Government Association data validator tool</a> on 2019-07-09.
<br /><br />
</main>

<script>
  // Fixes to dynamic elements created by DataTables to improve accessibility
  var removeElFn = setInterval(removeElement, 1000);
  
  function removeElement() {
    try {
      var el = document.getElementsByClassName("dataTables_scrollBody")[0].childNodes[0];
      el.removeChild(el.childNodes[0]); // Remove unwanted hidden text element from table - causing accessibility alert as it has no label
      
      el.parentNode.setAttribute('tabindex', '0');  // add attribute allowing keyboard users to access scrollable area
      
      clearInterval(removeElFn);  // cancel any further calls to this function as we have completed all actions
    }
    catch(e) {
      // form element 'el' doesn't exist yet so setInterval will call the function again until it does
    }
  }
</script>